---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# quaketools

<!-- badges: start -->
<!-- badges: end -->

The goal of quaketools is to provide a collection of tools to make earthquake modelling easier. Functions will be provided to simulate from, estimate and evaluate common models used in statistical seismology.

## Installation

You can install the development version of quaketools from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("zakvarty/quaketools")
```

## Example

This is a basic example which shows you how to simulate random variates from a generalised Pareto distribution using `rgpd()`.

```{r rgpd-example}
library(quaketools)
set.seed(4321)
rgpd(n = 10, scale = 1, shape = 0, shift = 0)
```
While this is equivalent to using `rexp()`, the seeding is not handled in the same way. In the following example we get two distinct samples from the standard exponential distribution. 

```{r rgpd-vs-rexp}
set.seed(1234)
rgpd_sample <- rgpd(n = 500, scale = 1, shape = 0, shift = 0)

set.seed(1234)
rexp_sample <- rexp(n = 500, rate = 1)


qqplot(
  x = rexp_sample,
  y = rgpd_sample, 
  xlim = c(0,8),
  ylim = c(0,8), 
  pch = 16,
  col = rgb(0,0,0,0.3))
abline(a = 0, b = 1, col = "darkorange")
```
